\documentclass[twocolumn, a4j]{ltjsarticle}
\usepackage{graphicx}
\usepackage[colorlinks, linkcolor=blue, bookmarksnumbered]{hyperref}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage[nameinlink]{cleveref}
\usepackage[subrefformat=parens]{subcaption}
\usepackage[top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}

\newcommand{\Cite}[1]{$^{\cref{#1}}$}

\crefformat{section}{#2第#1章#3}
\crefformat{subsection}{#2第#1節#3}
\crefformat{enumi}{#2(#1)#3}
\crefname{figure}{図}{図}
\crefname{table}{表}{表}
\crefname{equation}{式}{式}
\newcommand{\crefrangeconjunction}{-}
\newcommand{\crefrangepreconjunction}{}
\newcommand{\crefrangepostconjunction}{}
\newcommand{\crefpairconjunction}{、}
\newcommand{\crefmiddleconjunction}{、}
\newcommand{\creflastconjunction}{、}
\newcommand{\crefpairgroupconjunction}{、}
\newcommand{\crefmiddlegroupconjunction}{、}
\newcommand{\creflastgroupconjunction}{、}

\sisetup{inter-unit-product=\ensuremath{{}\cdot{}}}
\newcommand{\SII}[2]{\SI{#1}{[#2]}}

\title{粒子法FLOSSに対する妥当性確認試験 \\ Validation for Particle Method FLOSS}

\author{吉藤尚生、大友広幸 \\
	株式会社フィックスターズ \\
	東京都品川区大崎1-11-1 \\
	E-mail：yoshifuji@fixstars.com}

\date{2019年10月28日（第33回数値流体力学シンポジウム向け原稿）}

\begin{document}
\maketitle

\begin{abstract}
We created three benchmark problems to validate FLOSS of the Particle Method.
The targets were DualSPHysics and OpenMPS, which are mainly aim to apply in coastal and ocean engineering.
The first benchmark, the Central Gravity problem, validates the hydrostatic pressure.
It found that DualSPHysics is not able to solve the hydrostatic problem due to its density formulation.
It also found that MPS-GC method causes nonphysical surface oscillation due to nonconservation of momentum.
The second and third benchmarks are based on the Dambreak problem.
They validate the time series of the surface shape, water depth, and pressure.
The benchmark results showed that MPS-SPP is necessary to reduce the pressure fluctuation.
We continue to develop and invoke verification and validation for Particle Method FLOSS.
\end{abstract}

\input{main.tex}
\end{document}
